Treatment heterogeneity in comparative effectiveness of teriparatide vs bisphosphonates: multi-database cohort study

### 2021-02-23 submission/manuscript.rmd
fix naming to manuscript

---
title: "Treatment heterogeneity in comparative effectiveness of teriparatide vs bisphosphonates: multi-database cohort study"
output:
    bookdown::pdf_document2: default
    bookdown::word_document2:
        reference_docx: reference.docx
geometry: margin=1.0in
toc: false
font-size: 11pt
header-includes:
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage[left]{lineno}
  - \linenumbers
---

@@

For each outcome we used the derived prediction models to divide the population under study in 4 equally-sized subgroups, based on the quarters of the predicted risk distribution. Within each of these risk-based subgroups we developed a new propensity score model. Our analyses were performed on the propensity score matched (1 to 4) subset of the risk subgroup subset. We derived relative effect estimates using Cox proportional hazards models only with treatment as a predictor. Absolute effect estimates were calculated based on the difference of the Kaplan-Meier estimates.

# Results
A total of 758,879 patients were initially considered for our analyses. Of those, 18,809 received teriparatide and 740,070 received an oral bisphosphonate. Table 1 presents the patients considered in the final analyses across the 3 databases, after excluding patients experiencing the outcomes under study any time prior to cohort inclusion.

>>>>

---
title: "Treatment heterogeneity in comparative effectiveness of teriparatide vs bisphosphonates: multi-database cohort study"
output:
    bookdown::pdf_document2: default
    bookdown::word_document2:
        reference_docx: reference.docx
geometry: margin=1.0in
toc: false
font-size: 11pt
header-includes:
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage[left]{lineno}
  - \linenumbers
editor_options: 
  chunk_output_type: console
---

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
```

@@

For each outcome we used the derived prediction models to divide the population under study in 4 equally-sized subgroups, based on the quarters of the predicted risk distribution. Within each of these risk-based subgroups we developed a new propensity score model. Our analyses were performed on the propensity score matched (1 to 4) subset of the risk subgroup subset. We used a set of XXX negative control outcomes, to calibrate our results for unmeasured confounding (##REFEFRENCE). We derived relative effect estimates using Cox proportional hazards models only with treatment as a predictor. Absolute effect estimates were calculated based on the difference of the Kaplan-Meier estimates.

# Results

```{r, echo=FALSE}
incidenceOverall <- readRDS(here::here("data/raw/incidenceOverall.rds")) %>%
  dplyr::filter(analysisType == "matchOnPs_1_to_4") %>%
  dplyr::group_by(database) %>%
  dplyr::summarise(
    maxTreatment = max(treatmentPersons),
    maxComparator = max(comparatorPersons),
    .groups = "drop"
  )
```

<!-- Need to fix the numbers. See icpe abstract -->
A total of `r sum(incidenceOverall$maxTreatment) + sum(incidenceOverall$maxComparator)` patients were initially considered for our analyses. Of those, `r sum(incidenceOverall$maxTreatment)` received teriparatide and `r sum(incidenceOverall$maxComparator)` received an oral bisphosphonate. Table 1 presents the patients considered in the final analyses across the 3 databases, after excluding patients experiencing the outcomes under study any time prior to cohort inclusion.

```{r, echo=FALSE}
readRDS(here::here("data/raw/mappedOverallResultsNegativeControls.rds")) %>%
  dplyr::filter(analysisType == "matchOnPs_1_to_4") %>%
  head()
```
